An open and continuously updated fern tree of life (FTOL)

### 2022-02-04 ms/manuscript.Rmd
Update MS

genbank_plot <-
	ggplot(gb_species_by_year, aes(x = year, y = n_species)) +
	geom_line(aes(color = type), size = .7) +
	scale_color_manual(values = compartment_cols, guide = "none") +
	geom_label_repel(
		data = compartment_labs %>% filter(type %in% c("nuclear", "mitochondrial")),
		aes(color = type, label = label),
		segment.linetype = 2, 
		xlim = c(2020, Inf),
    # Do not repel from top or bottom edges.
    ylim = c(-Inf, Inf)
	) +
	geom_label_repel(
		data = compartment_labs %>% filter(type %in% c("total", "plastid")),
		aes(color = type, label = label),
		segment.linetype = 2, 
		xlim = c(2020, Inf),
    # Do not repel from top or bottom edges.
    ylim = c(-Inf, Inf),
		min.segment.length = 0
	) +
	geom_point(
		data = fern_tree_sampling,
		aes(shape = source),
		size = 2.5,
	) +
	labs(shape = "Study", y = "No. species", x = "Year") +
	theme(legend.position = "bottom") +
	coord_cartesian(clip = "off")
```

@@

```{r genbank-print, fig.width = 3.3, fig.height = 5, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
genbank_plot
```

>>>>

genbank_plot <-
	ggplot(gb_species_by_year, aes(x = year, y = n_species)) +
	geom_line(aes(color = type)) +
	scale_color_manual(values = compartment_cols, guide = "none") +
	geom_label_repel(
		data = compartment_labs %>% filter(type %in% c("nuclear", "mitochondrial")),
		aes(color = type, label = label),
		segment.linetype = 2, 
		xlim = c(2020, Inf),
    # Do not repel from top or bottom edges.
    ylim = c(-Inf, Inf)
	) +
	geom_label_repel(
		data = compartment_labs %>% filter(type %in% c("total", "plastid")),
		aes(color = type, label = label),
		segment.linetype = 2, 
		xlim = c(2020, Inf),
    # Do not repel from top or bottom edges.
    ylim = c(-Inf, Inf),
		min.segment.length = 0
	) +
	geom_point(
		data = fern_tree_sampling,
		aes(shape = source)
	) +
	labs(shape = "Study", y = "No. species", x = "Year") +
	theme(legend.position = "bottom",
				plot.margin = margin(r = 1, t = 0.5, unit = "in")) +
	coord_cartesian(clip = "off")
```

@@

```{r genbank-print, fig.width = 7, fig.height = 5, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
genbank_plot
```
